---
title: "PCAP Sample Analysis"
author: "John Reinier"
date: "`r Sys.Date()`"
knit: (function(input_file, encoding) {
    out_dir <- 'docs';
    rmarkdown::render(input_file,
      encoding=encoding,
      output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r lib, include=FALSE}
library(spsurvey)
library(RPostgres)
```

```{r conn, include=FALSE}
#open the connection
dw <- config::get("datawarehouse")

conn <- DBI::dbConnect(odbc::odbc(),
                      Driver = dw$driver,
                      Server = dw$server,
                      UID    = dw$uid,
                      PWD    = dw$pwd,
                      Port   = dw$port,
                      Database = dw$database
)
```

```{r ,include=TRUE}
framearea <- c('Bedford_Reservation'=2272.3, 'Brecksville_Reservation'=3488.4, 'Hinckley_Reservation'=2819.3, 'Mill_Stream_Run_Reservation'=3185.0, 'North_Chagrin_Reservation'=2173.9, 'Rocky_River_Reservation'=2588.7, 'South_Chagrin_Reservation'=1529.9, 'MinorRes'=3243.1, 'Prim_Bedford'=10677.0, 'Prim_Brecksville'=6142.4, 'Prim_Hinkley'=11773.2, 'Prim_Mill_Stream_Run'=10289.1, 'Prim_North_Chagrin'=6893.9, 'Prim_Rocky_River'=8754.2, 'Prim_South_Chagrin'=7408.5, 'Prim_South_Chagrin'=7408.5, 'Prim_MinorRes'=35501.9, 'Secondary'=32019.3, 'Seven_County'=1730283, 'LEAP_Region'=6589114)
```

## Import design file

```{r ,include=TRUE}
pcap.grts.design <- dbGetQuery(conn, 'SELECT * FROM survey_designs."Cleveland_Parks_Region_Sites" ORDER by id')
pcap.grts.design <- pcap.grts.design[c(-1,-2,-13,-22,-23,-24,-25,-26)]
head(pcap.grts.design,50)
```


## What are the strata and panels present?

```{r ,include=TRUE}
table(pcap.grts.design$stratum)
table(pcap.grts.design$panel)
table(pcap.grts.design$mdcaty)
```

## Check codes for Sampling Status & not use NN if present

```{r ,include=TRUE}
table(pcap.grts.design$EvalStatus)
tst <- pcap.grts.design$EvalStatus == 'NN'
pcap.grts.design <- pcap.grts.design[!tst,]
```

<div class="warning" style='padding:0.1em; background-color:#E9D8FD; color:#69337A'>
<span>
<p style='margin-top:1em; text-align:center'>
<b>Note on code meanings</b></p>
<p style='margin-left:1em;'>
TS - target and sampled site\
NT - non-target (i.e., not natural vegetation) and not sampled (replaced)\
NN - member of oversample and not needed (not evaluated)
</p>
</span>
</div>


## Adjust weights to match frame area
## Determine which sites to include in weight adjustment

```{r ,include=TRUE}
sites <- rep(TRUE,nrow(pcap.grts.design))
pcap.grts.design$final.wt <- adjwgt(pcap.grts.design$wgt,
                                    pcap.grts.design$mdcaty, framearea, sites)
```


## Check out weights
```{r ,include=TRUE}
tapply(pcap.grts.design$final.wt, pcap.grts.design$EvalStatus, sum)
```

# Estimation

##### Read in data files (pcap.grts.design) from weight adjustment process above

```{r ,include=FALSE}
pcap.grts.design_data1 <- dbGetQuery(conn, 'SELECT * FROM survey_designs.pcap_grts_data_first_sample ORDER by "siteID"')

pcap.grts.design_data2 <- dbGetQuery(conn, 'SELECT * FROM survey_designs.pcap_grts_data_second_sample ORDER by "siteID"')
```

# SAMPLE 1 ANALYSIS

##### Do estimates for FQAI and other metrics of interest
##### select which sites to use - only TS-target sampled sites
##### Set up sites, subpop, dsgn, and data data frames for estimation functions

##### sites identifies which sites to use in estimation
##### sites must have siteID and column indicating if site will be used

```{r ,include=TRUE}
sites.1 <- data.frame(siteID=pcap.grts.design_data1$siteID, 
                    Use=pcap.grts.design_data1$EvalStatus=='TS')

sites.2 <- data.frame(siteID=pcap.grts.design_data2$siteID, 
                      Use=pcap.grts.design_data2$EvalStatus=='TS')
```

```{r ,include=TRUE}
pcap.grts.design_data1 <- transform(pcap.grts.design_data1, final.wt=as.numeric(final.wt))

pcap.grts.design_data2 <- transform(pcap.grts.design_data2, final.wt=as.numeric(final.wt))

sapply(pcap.grts.design_data1, class)

sapply(pcap.grts.design_data2, class)
```

## Specify design information

```{r ,include=TRUE}
dsgn.1 <- data.frame(siteID=pcap.grts.design_data1$siteID,
                   stratum=pcap.grts.design_data1$stratum, 
                   wgt=pcap.grts.design_data1$final.wt,
                   xcoord=pcap.grts.design_data1$xcoord,
                   ycoord=pcap.grts.design_data1$ycoord)

dsgn.2 <- data.frame(siteID=pcap.grts.design_data2$siteID,
                     stratum=pcap.grts.design_data2$stratum, 
                     wgt=pcap.grts.design_data2$final.wt,
                     xcoord=pcap.grts.design_data2$xcoord,
                     ycoord=pcap.grts.design_data2$ycoord)
```

## Analysis of continuous variables

```{r ,include=TRUE}
ScoresSum.all.1 <- cont_analysis(
  pcap.grts.design_data1, 
  vars = c("fqai_score", "sensitive_rel_cov_metric_value", "tolerant_rel_cov_metric_value", "subcanopy_iv", "canopy_iv"), 
  subpop=NULL, 
  weight = "final.wt",                            
  xcoord = "xcoord", 
  ycoord = "ycoord", 
  pctval=c(5, 10, 25, 50, 75, 90, 95),
  conf=95,
  vartype='Local')

ScoresSum.subpop.1 <- cont_analysis(
  pcap.grts.design_data1, 
  vars = c("fqai_score", "sensitive_rel_cov_metric_value", "tolerant_rel_cov_metric_value", "subcanopy_iv", "canopy_iv"), 
  subpops = c("mdcaty", "group_description"), 
  weight = "final.wt", 
  xcoord = "xcoord", 
  ycoord = "ycoord", 
  pctval=c(5, 10, 25, 50, 75, 90, 95),
  conf=95,
  vartype='Local')

ScoresSum.all.2 <- cont_analysis(
  pcap.grts.design_data2, 
  vars = c("fqai_score", "sensitive_rel_cov_metric_value", "tolerant_rel_cov_metric_value", "subcanopy_iv", "canopy_iv"), 
  subpop=NULL, 
  weight = "final.wt",                            
  xcoord = "xcoord", 
  ycoord = "ycoord", 
  pctval=c(5, 10, 25, 50, 75, 90, 95),
  conf=95,
  vartype='Local')

ScoresSum.subpop.2 <- cont_analysis(
  pcap.grts.design_data2, 
  vars = c("fqai_score", "sensitive_rel_cov_metric_value", "tolerant_rel_cov_metric_value", "subcanopy_iv", "canopy_iv"), 
  subpops = c("mdcaty", "group_description"), 
  weight = "final.wt", 
  xcoord = "xcoord", 
  ycoord = "ycoord", 
  pctval=c(5, 10, 25, 50, 75, 90, 95),
  conf=95,
  vartype='Local')
```

<div class="warning" style='padding:0.1em; background-color:#E9D8FD; color:#69337A'>
<span>
<p style='margin-top:1em; text-align:center'>
<b>Can use R to Plot CDF estimates using function: cdfplot.fcn</b></p>
<p style='margin-left:1em;'>
File: cdfplot.fcn.r\
Programmer: Tony Olsen\
Date: Sept 23, 2002\
Input:\
cdfest - dataframe with x-value for cdf plot, y-value (cdf estimate)\
lower confidence bound\
upper confidence bound\
Output:\
plot of cdf with confidence bounds
</p>
</span>
</div>

```{r ,include=TRUE}
cdfplot.fcn <- function(cdfest,prop=T,...){
  
  if(prop == T) {
    plot(cdfest[,1],cdfest[,2]  ,
         type='l',ylim=c(0,100),...)
    tvalue <- cdfest[,2]>=5 & cdfest[,2]<=95
  }
  else {
    plot(cdfest[,1],cdfest[,2],type='l',...)
    tvalue <- cdfest[,2]>=0.05*max(cdfest[,2]) & 
      cdfest[,2]<=0.95*max(cdfest[,2])
  }
  value <- cdfest[,1][tvalue]
  upper <- cdfest[,4][tvalue]
  lower <- cdfest[,3][tvalue]
  lines(value,lower,lty=2)
  lines(value,upper,lty=2)
  
  legend(x=min(cdfest[,1]),y=max(cdfest[,2]),
         legend=c('CDF estimate','95% Confidence Limits'),
         lty=c(1,2), bty='n', cex=.7)
}
```
## All sites CDF estimates

```{r ,include=TRUE}
tsttype.all.1 <- ScoresSum.all.1$CDF$Subpopulation=='All Sites'
tsttype.all.2 <- ScoresSum.all.2$CDF$Subpopulation=='All Sites'
```

## Plot FQAI Score CDFs

```{r ,include=TRUE}
par(mfrow = c(2, 2))

tst.all.1 <- tsttype.all.1 & ScoresSum.all.1$CDF$Indicator=='fqai_score'
cdf.all.1 <- ScoresSum.all.1$CDF[tst.all.1,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.all.1,prop=T,xlab=xlab,ylab=ylab)
title('FQAI - All Sites - First Sample')
segments(x0 = 19.7, y0 = 0, x1 = 19.7, y1 = 56.5,
         col = "red",
         lwd = 3,
         lty = "dotted")
segments(x0 = 0, y0 = 56.5, x1 = 19.7, y1 = 56.5,
         col = "red",
         lwd = 3,
         lty = "dotted")
segments(x0 = 23.5, y0 = 0, x1 = 23.5, y1 = 77.5,
         col = "red",
         lwd = 3,
         lty = "dotted")
segments(x0 = 0, y0 = 77.5, x1 = 23.5, y1 = 77.5,
         col = "red",
         lwd = 3,
         lty = "dotted")
segments(x0 = 27.3, y0 = 0, x1 = 27.3, y1 = 91.3,
         col = "red",
         lwd = 3,
         lty = "dotted")
segments(x0 = 0, y0 = 91.3, x1 = 27.3, y1 = 91.3,
         col = "red",
         lwd = 3,
         lty = "dotted")
segments(x0 = 31.1, y0 = 0, x1 = 31.1, y1 = 97.9,
         col = "red",
         lwd = 3,
         lty = "dotted")
segments(x0 = 0, y0 = 97.9, x1 = 31.1, y1 = 97.9,
         col = "red",
         lwd = 3,
         lty = "dotted")


tst.all.2 <- tsttype.all.2 & ScoresSum.all.2$CDF$Indicator=='fqai_score'
cdf.all.2 <- ScoresSum.all.2$CDF[tst.all.2,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.all.2,prop=T,xlab=xlab,ylab=ylab)
title('FQAI - All Sites - Second Sample')
segments(x0 = 19.7, y0 = 0, x1 = 19.7, y1 = 56.5,
         col = "red",
         lwd = 3,
         lty = "dotted")
segments(x0 = 0, y0 = 56.5, x1 = 19.7, y1 = 56.5,
         col = "red",
         lwd = 3,
         lty = "dotted")
segments(x0 = 23.5, y0 = 0, x1 = 23.5, y1 = 77.5,
         col = "red",
         lwd = 3,
         lty = "dotted")
segments(x0 = 0, y0 = 77.5, x1 = 23.5, y1 = 77.5,
         col = "red",
         lwd = 3,
         lty = "dotted")
segments(x0 = 27.3, y0 = 0, x1 = 27.3, y1 = 91.3,
         col = "red",
         lwd = 3,
         lty = "dotted")
segments(x0 = 0, y0 = 91.3, x1 = 27.3, y1 = 91.3,
         col = "red",
         lwd = 3,
         lty = "dotted")
segments(x0 = 31.1, y0 = 0, x1 = 31.1, y1 = 97.9,
         col = "red",
         lwd = 3,
         lty = "dotted")
segments(x0 = 0, y0 = 97.9, x1 = 31.1, y1 = 97.9,
         col = "red",
         lwd = 3,
         lty = "dotted")
```

## Reservation Category cdf estimates

```{r ,include=TRUE}
par(mfrow = c(2, 2))

tsttype.subpop.1 <- ScoresSum.subpop.1$CDF$Subpopulation=='Bedford_Reservation'
# Plot FQAI Score CDFs for percent and area
tst.subpop.1 <- tsttype.subpop.1 & ScoresSum.subpop.1$CDF$Indicator=='fqai_score'
cdf.subpop.1 <- ScoresSum.subpop.1$CDF[tst.subpop.1,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.subpop.1,prop=T,xlab=xlab,ylab=ylab)
title('FQAI Score - Bedford Sample 1')

tsttype.subpop.2 <- ScoresSum.subpop.2$CDF$Subpopulation=='Bedford_Reservation'
# Plot FQAI Score CDFs for percent and area
tst.subpop.2 <- tsttype.subpop.2 & ScoresSum.subpop.2$CDF$Indicator=='fqai_score'
cdf.subpop.2 <- ScoresSum.subpop.2$CDF[tst.subpop.2,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.subpop.2,prop=T,xlab=xlab,ylab=ylab)
title('FQAI Score - Bedford Sample 2')

tsttype.subpop.1 <- ScoresSum.subpop.1$CDF$Subpopulation=='Brecksville_Reservation'
# Plot FQAI Score CDFs for percent and area
tst.subpop.1 <- tsttype.subpop.1 & ScoresSum.subpop.1$CDF$Indicator=='fqai_score'
cdf.subpop.1 <- ScoresSum.subpop.1$CDF[tst.subpop.1,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.subpop.1,prop=T,xlab=xlab,ylab=ylab)
title('FQAI - Brecksville Sample 1')

tsttype.subpop.2 <- ScoresSum.subpop.2$CDF$Subpopulation=='Brecksville_Reservation'
# Plot FQAI Score CDFs for percent and area
tst.subpop.2 <- tsttype.subpop.2 & ScoresSum.subpop.2$CDF$Indicator=='fqai_score'
cdf.subpop.2 <- ScoresSum.subpop.2$CDF[tst.subpop.2,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.subpop.2,prop=T,xlab=xlab,ylab=ylab)
title('FQAI Score - Brecksville Sample 2')

tsttype.subpop.1 <- ScoresSum.subpop.1$CDF$Subpopulation=='Hinckley_Reservation'
# Plot FQAI Score CDFs for percent and area
tst.subpop.1 <- tsttype.subpop.1 & ScoresSum.subpop.1$CDF$Indicator=='fqai_score'
cdf.subpop.1 <- ScoresSum.subpop.1$CDF[tst.subpop.1,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.subpop.1,prop=T,xlab=xlab,ylab=ylab)
title('FQAI - Hinckley Sample 1')

tsttype.subpop.2 <- ScoresSum.subpop.2$CDF$Subpopulation=='Hinckley_Reservation'
# Plot FQAI Score CDFs for percent and area
tst.subpop.2 <- tsttype.subpop.2 & ScoresSum.subpop.2$CDF$Indicator=='fqai_score'
cdf.subpop.2 <- ScoresSum.subpop.2$CDF[tst.subpop.2,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.subpop.2,prop=T,xlab=xlab,ylab=ylab)
title('FQAI Score - Hinckley Sample 2')

tsttype.subpop.1 <- ScoresSum.subpop.1$CDF$Subpopulation=='Mill_Stream_Run_Reservation'
# Plot FQAI Score CDFs for percent and area
tst.subpop.1 <- tsttype.subpop.1 & ScoresSum.subpop.1$CDF$Indicator=='fqai_score'
cdf.subpop.1 <- ScoresSum.subpop.1$CDF[tst.subpop.1,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.subpop.1,prop=T,xlab=xlab,ylab=ylab)
title('FQAI - Mill Stream Run Sample 1')

tsttype.subpop.2 <- ScoresSum.subpop.2$CDF$Subpopulation=='Mill_Stream_Run_Reservation'
# Plot FQAI Score CDFs for percent and area
tst.subpop.2 <- tsttype.subpop.2 & ScoresSum.subpop.2$CDF$Indicator=='fqai_score'
cdf.subpop.2 <- ScoresSum.subpop.2$CDF[tst.subpop.2,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.subpop.2,prop=T,xlab=xlab,ylab=ylab)
title('FQAI Score - Mill Stream Run Sample 2')

tsttype.subpop.1 <- ScoresSum.subpop.1$CDF$Subpopulation=='North_Chagrin_Reservation'
# Plot FQAI Score CDFs for percent and area
tst.subpop.1 <- tsttype.subpop.1 & ScoresSum.subpop.1$CDF$Indicator=='fqai_score'
cdf.subpop.1 <- ScoresSum.subpop.1$CDF[tst.subpop.1,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.subpop.1,prop=T,xlab=xlab,ylab=ylab)
title('FQAI - North Chagrin Sample 1')

tsttype.subpop.2 <- ScoresSum.subpop.2$CDF$Subpopulation=='North_Chagrin_Reservation'
# Plot FQAI Score CDFs for percent and area
tst.subpop.2 <- tsttype.subpop.2 & ScoresSum.subpop.2$CDF$Indicator=='fqai_score'
cdf.subpop.2 <- ScoresSum.subpop.2$CDF[tst.subpop.2,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.subpop.2,prop=T,xlab=xlab,ylab=ylab)
title('FQAI - North Chagrin Sample 2')

tsttype.subpop.1 <- ScoresSum.subpop.1$CDF$Subpopulation=='Rocky_River_Reservation'
# Plot FQAI Score CDFs for percent and area
tst.subpop.1 <- tsttype.subpop.1 & ScoresSum.subpop.1$CDF$Indicator=='fqai_score'
cdf.subpop.1 <- ScoresSum.subpop.1$CDF[tst.subpop.1,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.subpop.1,prop=T,xlab=xlab,ylab=ylab)
title('FQAI - Rocky River Sample 1')

tsttype.subpop.2 <- ScoresSum.subpop.2$CDF$Subpopulation=='Rocky_River_Reservation'
# Plot FQAI Score CDFs for percent and area
tst.subpop.2 <- tsttype.subpop.2 & ScoresSum.subpop.2$CDF$Indicator=='fqai_score'
cdf.subpop.2 <- ScoresSum.subpop.2$CDF[tst.subpop.2,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.subpop.2,prop=T,xlab=xlab,ylab=ylab)
title('FQAI - Rocky River Sample 2')

tsttype.subpop.1 <- ScoresSum.subpop.1$CDF$Subpopulation=='South_Chagrin_Reservation'
# Plot FQAI Score CDFs for percent and area
tst.subpop.1 <- tsttype.subpop.1 & ScoresSum.subpop.1$CDF$Indicator=='fqai_score'
cdf.subpop.1 <- ScoresSum.subpop.1$CDF[tst.subpop.1,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.subpop.1,prop=T,xlab=xlab,ylab=ylab)
title('FQAI - South Chagrin Sample 1')

tsttype.subpop.2 <- ScoresSum.subpop.2$CDF$Subpopulation=='South_Chagrin_Reservation'
# Plot FQAI Score CDFs for percent and area
tst.subpop.2 <- tsttype.subpop.2 & ScoresSum.subpop.2$CDF$Indicator=='fqai_score'
cdf.subpop.2 <- ScoresSum.subpop.2$CDF[tst.subpop.2,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.subpop.2,prop=T,xlab=xlab,ylab=ylab)
title('FQAI - South Chagrin Sample 2')

tsttype.subpop.1 <- ScoresSum.subpop.1$CDF$Subpopulation=='MinorRes'
# Plot FQAI Score CDFs for percent and area
tst.subpop.1 <- tsttype.subpop.1 & ScoresSum.subpop.1$CDF$Indicator=='fqai_score'
cdf.subpop.1 <- ScoresSum.subpop.1$CDF[tst.subpop.1,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.subpop.1,prop=T,xlab=xlab,ylab=ylab)
title('FQAI - Minor Res Sample 1')

tsttype.subpop.2 <- ScoresSum.subpop.2$CDF$Subpopulation=='MinorRes'
# Plot FQAI Score CDFs for percent and area
tst.subpop.2 <- tsttype.subpop.2 & ScoresSum.subpop.2$CDF$Indicator=='fqai_score'
cdf.subpop.2 <- ScoresSum.subpop.2$CDF[tst.subpop.2,c('Value','Estimate.P','LCB95Pct.P','UCB95Pct.P')]
xlab <- 'FQAI Score'
ylab <- 'Percent'
cdfplot.fcn(cdf.subpop.2,prop=T,xlab=xlab,ylab=ylab)
title('FQAI - Minor Res Sample 2')
```


